Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-09-13 inst/examples/20160715-Krakow-Fennica.Rmd
slide template paper cons fix

# Remove entries outside the investigated publication periods
df <- df %>% filter(!is.na(period)) %>% group_by(period, paper)
df <- df %>% summarise(n = n(),
		  paper2 = sum(paper, na.rm = TRUE)) %>%
             mutate(paper.per.title = paper2/n)		 
df$paper <- df$paper2
df$paper2 <- NULL

>>>>

# Remove entries outside the investigated publication periods
df <- df %>% filter(!is.na(period)) %>% group_by(period)
df <- df %>% summarise(n = n(),
		  paper2 = sum(paper, na.rm = TRUE)) %>%
             mutate(paper.per.title = paper2/n)		 
df$paper <- df$paper2
df$paper2 <- NULL
